\input{HeadMatter.tex}
	
\begin{flushleft}
\Large\textbf{Assignment 3 (10\%)- Manage Notes Production}\\
\end{flushleft}

In this assignment you will manage the production of lecture notes for normal class lecture.  The process will involve determining the content of the notes, delegating the content production to the class team, managing the production process and assembling the final documentation.  Each class member will be assigned a lecture to manage.  All class members are expected to actively contribute to the work.\\

\textbf{Key Information}\\

\begin{itemize}
	\item Trello (\href{trello.com}{trello.com}) will be used to manage the production process
	\item The final notes are to take the form of a digital submission.  The exact format, .docx, .pptx, .pdf, etc. is at the managers discretion. 
	\item Final documentation will normally be submitted 3 weeks after the lecture is given.  A schedule of submission dates has been provided on Google Sheets at \href{https://goo.gl/L2KXkq}{https://goo.gl/L2KXkq}
	\item The final notes will be submitted via Moodle, and published on Moodle sometime after.
	\item 50\% of the mark awarded will be based on the teams evaluation of the manger.  Scoring criteria is detailed later.
\end{itemize}

\textbf{General Guidelines for all participants}\\

\begin{itemize}
	\item Managers Manage: they are not permitted to undertake the work.
	\item Managers can format and style the content provided to them; they cannot edit
	\item Managers are responsible for Delegation, Motivation, Quality Control, and are entitled to request feedback and status updates as they deem necessary
	\item Team Members do the work
	\item Team Members are required to provide status updates and feedback on the work they have been allocated
	\item Team Members retain ownership of the tasks allocated to them. 
	\item Lecturer will provide technical support to Team Members
	\item Lecturer will provide management support to the Manager
\end{itemize}

\textbf{Manager Scoring Criteria}\\
Each team member will score the managers performance out of 10, based on the following critera.  All elements should be given an equal weighting.

\begin{itemize}
	\item Team co-operation
	\item Clarity of delegation and task requirements
	\item Team Productivity
	\item Team Sentiment
\end{itemize}

A Google Form has been created to collect this data.  Please note that evaluations are private but not anonymous





\textbf{Submission}\\
Your completed website and documentation are to be zipped into a single file\footnote{Your zip file should preserve you folder structure} and uploaded to Moodle on or before the date and time indicated.  Key aspects of the submission are:
\begin{itemize}
	\item Your report should be submitted in pdf format only.  \textsc{Do Not Submit Word Documents}.
	\item The zip file should contain all licenses included with any third party assets that you use.  Downloaded material, where possible, should be kept in its original format and included in a subdirectory of the relevant section.  (Fonts are typically downloaded as a zip file)
	\item Your presentation should be included in a separate folder.
\end{itemize}




\textbf{Late Submission}\\
Failure to submit your assignment on or before the date and time indicated on Moodle will result in a penalty of 5\% per day or part thereof.  Moodle will not accept late submissions 5 minutes before the first presentation is due to commence.  You will have to speak to me directly if you miss this deadline.

\vspace{0.5cm}
\textbf{Marking Scheme}\\

\begin{table}[h!]
     \begin{center}
     \begin{tabular}{p{7cm}  p{3cm} }
     \toprule
      \textbf\large{Element} & \textbf\large{Proportion} \\ 
    \cmidrule(r){1-1}\cmidrule(lr){2-2}
      \textbf{Team Evaluation} & \textbf{50\%}\\
      \textbf{Lecturer Evaluation} & \textbf{50\%}\\    
      \\ \bottomrule
      \end{tabular}
      \label{tbl:markSchemeAsmt3}
      \end{center}
 \end{table}

\end{document}