\input{HeadMatter.tex}

\begin{flushleft}
\Large\textbf{Assignment 4 - Your own Object (15\%)}\\
\end{flushleft}

In this assignment you will model, render and 3D print a simple ornamental object of your own selection.  I will advise you on your object selection.  Ceramic objects are normally a good choice from both a modelling and rendering perspective. This assignment will test your ability to model, apply materials and render.  Additionally, you will create a 3D print of your final model.  Your work-flow will be:
\begin{enumerate}
	\item Create studio photos of your object. I will assist in this aspect.
	\item Create a low-poly model of your object.
	\item Once the geometric modelling is complete you should consider 3D printing it.
	\item Use UWV mapping to correctly apply a material of your own creation to the model.
	\item Import your model into the 3DS photographic studio template.
	\item Create a selection of photo-realistic V-Ray renders (png or jpg of approx 4k resolution) of your object.
\end{enumerate}

You will are required to produce 5 photorealistic images of your object from various viewpoints.  You are also required to produce a simple A2 poster.  If you wish you can produce your images at a photoprinters, and paste those images to a black background.\\

Your poster should showcase your model using the 5 photo-realistic images as well as a number of technical images.  Typical technical images are checker renders, AO renders and shaded wire-frame renders. 

The digital Submission is to be a zip file containing your 3DS project folder including the model geometry, materials, and rendered images.  The 3D print files (.stl, .gcode and .wtk) are also to be included in the submission pack.  \\

The physical submission (3D print and poster) are to be handed over at the next class session following the submission.


\vspace{0.5cm}

\input{LateSubmission.tex}

\end{document}